\section{Problem 3}

\subsection{Solution}
A randomly selected student in an engineering class id diligent with probability $0.3$, and lazy with probability $0.7$. A diligent student completes all of her homework with probability $0.9$ and does not do so with probability $0.1$. Meanwhile, a lazy student completes all homework with probability $0.5$ and does not do so with probability $0.5$. A student who completes all homework receives an $A$ grade with probability $0.6$, and receives a $B$ grade with probability $0.4$ (irrespective of whether the student was diligent or lazy). A student who doesn't complete all homework receives an $A$ grade with probability $0.3$, a $B$ grade withe probability $0.4$ and an $F$ grade with probability $0.3$ (again, irrespective of whether the student was diligent or lazy).\\
Please answer the following questions.\\

\begin{enumerate}[a.]
	\item What is the probability that a randomly selected student is diligent, completes all their homework and receives an $A$ grade?
	\item What is the probability that the student completes all of their homework?
	\item What is the probability that the student receives an $A$ grade?
	\item Given that a randomly selected student completed all their homework, what is the probability that the student was lazy?
	\item Given that a randomly-selected student received an $A$ grade, what is the probability that the student is lazy?
	\item Is the event that a student passes the course (receives an $A$ or $B$ grade) independent of the event that the student is lazy?
	\item Is the event that a student receives a $B$ grade independent of the event that the student is lazy? 
\end{enumerate}

\subsection{Solution}
\noindent\rule{\textwidth}{1pt}